\newpage
\vspace{-1cm}
\chapter*{\zihao{-2}{ABSTRACT}}
\vspace{-0.5cm}
 Nowadays, software is widely used in various fields, but accidents caused by software problems also occur frequently. For rail transit, once an accident occurs, it may cause traffic paralysis and even threaten life and safety. Through the trustworthy quantitative evaluation of the whole life cycle of the completed rail transit interlocking software, the overall quality of the software and the perfection of the development process can be reflected more comprehensively, so as to realize the guidance of the future software development process. The laboratory team has carried out trustworthiness evaluation in the field of aerospace and nuclear equipment and applied it to practical projects previously. This paper studies another rail transit area in the field of safety. Therefore, the work of this paper revolves around the following three aspects:
 
 Firstly, a trustworthiness quantitative evaluation model of rail transit interlock software is established. Based on the four trusted attributes, this paper constructs trustworthy quantitative evaluation index system and structural equation model for the whole life cycle, and calculates the weight of the metric elements, sub-attributes and attributes accordingly; combines the formula of the trustworthiness measurement model to calculate the trustworthiness value of the sub-attributes, attributes, stages and the whole software; refers to the trustworthiness quantitative classification model table to determine the conditions satisfied by the trustworthiness value of the software, and to divide the trustworthiness level of the software.
 
 Secondly, based on the trustworthiness quantitative classification model table, two trustworthiness allocation algorithms are designed. The first algorithm allocates according to the priority index of metric element from high to low; the second is an allocation algorithm based on greedy selection strategy to calculate the minimum improvement cost needed to make the software reach a certain trustworthiness level.
 
 Finally, this paper develops a trustworthiness quantitative evaluation tool for rail transit interlocking software. The tool consists of three modules: basic information management module, whole life cycle trustworthiness evaluation module and evaluation result output module. The whole life cycle trustworthiness evaluation module is divided into four stages: requirement, design, coding and testing. Each sub-module has three functions: trusted evidence input, weight allocation and trustworthiness value calculation. The tool has been applied to the trustworthiness evaluation of Suzhou Rail Line 2 interlocking software developed by Fuxin Intelligent Control Company.

\vspace{0.5cm}
{\sihao{\textbf{Keywords:}}} \textit{Trustworthy Software; Rail Transit; Trustworthiness Evaluation Model; Trustworthiness Allocation; Quantitative Evaluation Tool}


































